---
title: "Risk Summary"
output: pdf_document
date: "`r format(Sys.Date(), '%B %d, %Y')`"
params:
  rpt_trnsf_text: NA
  rpt_stroke_text: NA
  rpt_aki_text: NA
  rpt_nrd_text: NA
  rpt_majbleed_text: NA
  rpt_mort_text: NA
  rpt_trnsf: NA
  rpt_stroke: NA
  rpt_aki: NA
  rpt_nrd: NA
  rpt_majbleed: NA
  rpt_mort: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(personograph)

gen_graph <- function(x){
  
  probs <- list(`Experience Event` = x,
                `Do Not Experience Event` = 1-x)
  
  suppressWarnings(
    personograph(probs, n.icons=1000, draw.legend = F, plot.width=1.0, dimensions=c(20,50), 
                 colors = list(`Experience Event` = "#B7202E",
                               `Do Not Experience Event` = "#BBBDC0"))
  )
}


```

## Summary

The rate of outcomes following PCI for similar patients is:

- `r paste(params$rpt_trnsf_text)`
- `r paste(params$rpt_stroke_text)`
- `r paste(params$rpt_aki_text)`
- `r paste(params$rpt_nrd_text)`
- `r paste(params$rpt_majbleed_text)`
- `r paste(params$rpt_mort_text)`

*Predictions are based only on patients not on dialysis at the time of PCI.

## Transfusion

`r paste(params$rpt_trnsf_text)`

```{r}
gen_graph(params$rpt_trnsf)
#\vspace*{-0.75cm}
```

\newpage

## Stroke

`r paste(params$rpt_stroke_text)`

```{r}
gen_graph(params$rpt_stroke)
# \vspace*{-0.75cm}
```

\newpage

## Acute Kidney Injury

`r paste(params$rpt_aki_text)`

```{r}
gen_graph(params$rpt_aki)
```

*Predictions are based only on patients not on dialysis at the time of PCI.

\newpage

## New Requirement for Dialysis

`r paste(params$rpt_nrd_text)`

```{r}
gen_graph(params$rpt_nrd)
```

*Predictions are based only on patients not on dialysis at the time of PCI.

\newpage

## Major Bleed

`r paste(params$rpt_majbleed_text)`

```{r}
gen_graph(params$rpt_majbleed)
```

\newpage

## Mortality

`r paste(params$rpt_mort_text)`

```{r}
gen_graph(params$rpt_mort)
```